15th International Satisfiability Modulo Theories Competition (SMT-COMP 2020): Rules and Procedures

### 2021-05-01 rules/rules21.tex
model syntax, single query track check

  \item {\bf The Strings Division is not experimental.}
    The last year's competition introduced a experimental divisions for benchmarks that
    use strings. This year, the String division is no longer experimental.

  \rationale{The final specification of the string theory has been officially released.}

  \item {\bf Model syntax in \mvaltrack.}  The syntax used in the
    model validation track did not conform to the SMTLIB standard.
    The difference is that the syntax used previously included an
    additional keyword \texttt{model} after the opening parenthesis in
    the output.  This year we support both the SMTLIB syntax and the
    old syntax.  We urge solver writers to upgrade their solver to use
    the new syntax.

@@

  \rationale{There were only small issues with these divisions, so there is no
    reason to keep it experimental. For the new divisions, as before, given the
    inconsistencies across different model producing solvers, we proceed in an
    experimental fashion to push for model standardization.}
\end{itemize}

>>>>

  \item {\bf Stricter checks for output in single query track.}
    It is now checked that the output in the single query track starts with
    sat or unsat.  Error messages before such an output is no longer ignored
    and are treated as an \texttt{unknown} result.
    {\bf Note:} Solver authors should make sure not to print any debugging
    output.  This includes debugging output on stderr, because the
    post-processors cannot distinguish between stderr and stdout.

  \rationale{A solver that does not support the full logic may
    report errors and then continue ignoring the failed assertion.  This
    way, it may be flagged as unsound under the old rules, even though it
    clearly indicated the error.}

@@

  \rationale{There were only small issues with these divisions, so there is no
    reason to keep it experimental. For the new divisions, as before, given the
    inconsistencies across different model producing solvers, we proceed in an
    experimental fashion to push for model standardization.}

  \item {\bf Model syntax in \mvaltrack.}  The syntax used in the
    model validation track did not conform to the SMT-LIB standard.
    The difference is that the syntax used previously included an
    additional keyword \texttt{model} after the opening parenthesis in
    the output.  This year we support both the SMT-LIB syntax and the
    old syntax.  We urge solver writers to upgrade their solver to use
    the new syntax.

    We added new tracks for UF logics. According to the SMT-LIB standard,
    model values of uninterpreted sorts should use the syntax
    \texttt{(as @name Sort)}.
    In particular the model validator needs to know the sort of the model
    value.  Furthermore, it is implicitly assumed that model values
    differ if they have different names.

\end{itemize}
